Stochastic Approximation Monte Carlo with a Dynamic Update Factor (SAD)

### 2019-01-09 papers/histogram/sad.tex
update gamma plot and some text about reference comparison choices.

We use the average entropy error vs moves as a metric to compare
simulation runtimes and overall convergence. The overall accuracy
is determined by examining the fractional error of a particular method to
a precise reference system. For each simulation, the reference system
is chosen to be the final output of the SAMC simulation with the best
choice of $t_0$.
\begin{align}
\epsilon_\text{avg} = 1 - \bigg\lvert\frac{S_\text{method}}{S_\text{ref}}\bigg\rvert
\end{align}
Simulations that take more iterations to reach the same entropy error as a
different method take longer to converge. This behavior is seen in
Fig.~\ref{fig:N50-ff0.3-avg-error}.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/3$ with
  SAMC $t_0 = 10^5$ serving as the reference.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-slow.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/3$ with
  SAMC $t_0 = 10^5$ from Fig.~\ref{fig:N50-ff0.3-avg-error}
  serving as the reference.}\label{fig:N50-ff0.3-avg-error-slow}
\end{figure}

>>>>

We use the average entropy error vs moves as a metric to compare
simulation runtimes and overall convergence. The overall accuracy
is determined by examining the fractional error of a particular method to
a precise reference system. For each simulation, the reference system
is chosen to be the final output of the SAMC simulation with the best
choice of $t_0$.
\begin{align}
\epsilon_\text{avg} = 1 - \bigg\lvert\frac{S_\text{method}}{S_\text{ref}}\bigg\rvert
\end{align}
Simulations that take more iterations to reach the same entropy error as a
different method take longer to converge. This behavior is seen in
Fig.~\ref{fig:N50-ff0.3-avg-error}.
\jpsays{We use a SAMC $t_0 = 10^3$ with a fixed energy range $S_{\max} = 120$ and $S_{\min} = 248$ as the reference.
This is noted because this is not strictly SAMC method. We use this as a reference to increase convergence time of the
reference.}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-default.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/3$ with
  a fixed energy range SAMC $t_0 = 10^3$ serving as the reference.}\label{fig:N50-ff0.3-avg-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error-slow.pdf}
  \caption{The average entropy error for each MC method is shown for $\eta = 0.3$ and $T_{\min} = 1/3$ with
  a fixed energy range SAMC $t_0 = 10^3$ from Fig.~\ref{fig:N50-ff0.3-avg-error}
  serving as the reference.}\label{fig:N50-ff0.3-avg-error-slow}
\end{figure}
